Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-24 poster/main.tex
fit middle column better

Replacing the summary of the past $s_{t-1}$ with a linear surrogate $\tilde{s}_{t-1}$
allows the easy adaption of any existing RNN architecture for parallel computation.
Several existing RNNs can be viewed as linear surrogate RNNs.
\vspace{1ex}

@@

\begin{block}{Accelerating Existing Linear Surrogate RNNs}
We compare the performance of several recent linear RNNs
implemented with the parallel linear recurrence kernel against
a baseline serial linear recurrence kernel.

\vspace{1ex}
\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrr}
\label{table:rnn-throughput}
\small{Seq.\ Len.} & \small{SRU} & \small{QRNN(2)}
  & \small{QRNN(10)} & \small{GILR-LSTM}\\ \midrule
16 & 0.28 & 0.38 & 0.78 & 0.61\\
256 & 0.84 & 0.86 & 0.99 & 0.91\\
4,096 & 1.38 & 1.18 & 1.05 & 0.98\\
65,536 & 9.21 & 6.68 & 2.05 & 1.41\\ \bottomrule
\end{tabular}
\end{center}
\vspace{2ex}
\caption{Parallel kernel speedup for a variety of LS-RNNs.   All models use two stacked RNN layers with 256 hidden
  units, keeping the GPU memory usage constant by fixing $bT = 65,536$
  for minibatch size $b$ and sequence length $T$. QRNN($k$) refers to a
  QRNN with filter size $k$. %\citep{bradbury2017quasi}
}
\end{table}
\end{block}

%----------------------------------------------------------------------------------------
\vspace{-1ex}
\begin{figure}
\includegraphics[width=0.9\linewidth]{cudnn_heatmap_gilr.png}
\caption{Throughput (thousand steps/s) for same sized LSTM and GILR-LSTM}
\end{figure}

@@

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Additional Information}

Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\end{itemize}

@@

\begin{block}{Acknowledgements}

\small{\rmfamily{Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\

>>>>

Replacing the summary of the past $s_{t-1}$ with a linear surrogate $\tilde{s}_{t-1}$
allows the easy adaption of any existing RNN architecture for parallel computation.
Several recent linear RNNs can be viewed as linear surrogate RNNs.
\vspace{1ex}

@@

\begin{block}{Training Runtime Results}
\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrr}
\label{table:rnn-throughput}
\small{Seq.\ Len.} & \small{SRU} & \small{QRNN(2)}
  & \small{QRNN(10)} & \small{GILR-LSTM}\\ \midrule
16 & 0.28 & 0.38 & 0.78 & 0.61\\
256 & 0.84 & 0.86 & 0.99 & 0.91\\
4,096 & 1.38 & 1.18 & 1.05 & 0.98\\
65,536 & 9.21 & 6.68 & 2.05 & 1.41\\ \bottomrule
\end{tabular}
\end{center}
\vspace{2ex}
\caption{Parallel kernel speedup compared to serial linear recurrence for a variety of LS-RNNs
  All models use two stacked RNN layers with 256 hidden
  units, keeping the GPU memory usage constant by fixing $bT = 65,536$
  for minibatch size $b$ and sequence length $T$. QRNN($k$) refers to a
  QRNN with filter size $k$. %\citep{bradbury2017quasi}
}
\end{table}
\end{block}

%----------------------------------------------------------------------------------------
\vspace{-1ex}
\begin{figure}
\includegraphics[width=0.9\linewidth]{cudnn_heatmap_gilr.png}
\caption{Throughput (thousand steps/s) for 2 layer 256 unit cuDNN LSTM and GILR-LSTM as
a function of batch size and sequence length. LSTM throughput is independent of sequence
length. GILR-LSTM can achieve much greater throughput at small batch sizes.}
\end{figure}

@@

@@
